\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[grey]{classic}
\usepackage[utf8]{inputenc}
% \usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Vyacheslav}
\familyname{Barinov}
\address{}{Moscow, Russia}
% \mobile{+7 ...}
\email{rayslava@gmail.com}
\homepage{https://github.com/rayslava}
\extrainfo{Software should be beautiful. Both inside and outside.}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Brief description}
\cvitem
  {}
  {My main direction - C/C++ Linux development.\newline{}
  This symbiosis allows me to create interacting system of a mobile client and a web service.\newline{}
  I really enjoy OpenSource software and do my best to develop and contribute OpenSource projects which I'm interested in.}

\section{OpenSource Projects}
\subsection{C++ / Qt}
\cvitem
  {Leechcraft}
  {\url{https://github.com/rayslava/leechcraft}\newline{}
  A modular internet client. My part is Twitter client plugin}
\subsection{C++}
\cvitem
  {Massacre}
  {\url{https://github.com/rayslava/Massacre}\newline{}
  A simple 3D engine}

\section{Commercial Projects}
  \subsection{C/C++ / Linux}
  \cvitem
    {Tizen}
    {\url{http://tizen.org}\newline{}
    Toolchain support}

\section{Experience}
\cventry
  {Feb 2012 - still here}
  {Software Engineer}
  {Samsung Research Russia, Moscow}
  {}{}
  {Software development and toolchain maintenance
  \newline{}Software development.}
\cventry
  {Feb 2011 - Oct 2012}
  {iOS/RubyOnRails developer}
  {MLSDev LLC. Donetsk, Ukraine}
  {}{}
  {Assessment of requirements for software development and time estimation. 
  \newline{}Software development.
  \newline{}Web-services deployment and support.}
\cventry
  {Aug 2010 - Feb 2011}
  {C++/Qt developer}
  {WiseTroll (Sole Proprietorship). Donetsk, Ukraine}
  {}{}
  {Assessment of requirements for software development and time estimation. 
  \newline{}Software development.}


\section{Development skills}
\subsection{Programming Languages}
\cvline
  {Expert}{Objective-C}
\cvline
  {Intermediate}{C, C++, Ruby, Bash}
\cvline
  {Basic}{Perl, LaTeX}
\subsection{Frameworks and tools}
\cvline{iOS}{CocoaPods, Cedar, Calabash-iOS, RestKit, CoreData}
\cvline{RubyOnRails}{Cucumber, RSpec, Rabl, Devise, CanCan, Twitter Bootstrap, Grape, Slim}

\section{Server administration skills}
\cvline
  {Redmine, GitLabHQ}{Deployment, support and migration to another servers (Debian, Ubuntu)}
\cvline
  {Jenkins}{Deployment and support on MacOS X}
\cvline
  {Nginx, Apache}{Setup and configuration on rpm- and deb-based linux systems}

\section{Computer skills}
  \cvline
  {IDE}{Xcode, Vim, QtCreator}
  \cvline
  {OS}{Linux (RedHat, Debian), MacOS X}
  \cvline
  {VCS}{Git, Mercurial}
  \cvline
  {Development technics}{BDD, TDD, XP, Continuous Integration}

\section{Education}
  \cventry
    {Oct 2006 - Dec 2011}
    {Software Development}
    {Computer Academy "Step", Donetsk, Ukraine}
    {}{}
    {Team member, represented Ukraine at the final of ImagineCup'10 at Poland.}
  \cventry
    {Sep 2006 - Jul 2010}
    {Management of Organizations, Bachelor}
    {Open International University of Human Development “Ukraine”}
    {}{}{}

\section{Public activity}
  \cvline{LinkedIn}{\url{http://www.linkedin.com/pub/alexey-denisov/2a/bab/a29}}
  \cvline{GitHub}{\url{https://github.com/AlexDenisov}}
  \cvline{CoderWall}{\url{http://coderwall.com/AlexDenisov}}
  \cvline{Habrahabr}{\url{http://habrahabr.ru/users/1101_debian/}}
  \cvline{RubyGems}{\url{https://rubygems.org/profiles/58746}}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
%%% Build: latex2html -split 0 -nonavigation  -init_file ~/work/btrwork/soft/moderncv2html/moderncv.perl cv.tex -info 0